---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# benjaminileaves

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/benjaminileaves)](https://CRAN.R-project.org/package=benjaminileaves)
<!-- badges: end -->

## Generate benjamini leaves with bezier curves

The goal of this package is to generate shapes in the form of ficus benjamina leaves ([weeping fig](https://en.wikipedia.org/wiki/Ficus_benjamina))
with bezier curves. To demonstrate it we'll first load some packages:


## Installation

You can install the released version of benjaminileaves from [CRAN](https://CRAN.R-project.org) with:

``` r
# install.packages("remotes")
# (if not installed yet)

remotes::install_github("urswilke/benjaminileaves")
```

## Usage

First load some libraries:

```{r loadlibs, message=FALSE}
library(benjaminileaves)
library(purrr)
library(dplyr)
library(tidyr)
library(ggplot2)
set.seed(123)
```

## Illustration of the generated data

The package generates bezier curves that imitate the shape of the leaves of a
ficus benjamini. The main function is `benjamini_leaf()` which results in a dataframe where i denotes the id of the bezier curve, and x & y point coordinates: 

```{r fun}
df <- benjamini_leaf()
df
```

The meaning is best illustrated with a plot:
```{r def}
segments <- df %>% 
  group_by(i) %>% 
  mutate(j = c(1, 2, 1, 2)) %>%
  ungroup() %>% 
  pivot_wider(
    names_from = j,
    values_from = c(x, y),
    values_fn = list
  ) %>% 
  unnest(c(x_1, x_2, y_1, y_2))


ggplot(df, aes(x = x, y = y)) + 
  geom_point(color = "red") +
  geom_point(data = df %>% group_by(i) %>% slice(c(1, 4)), color = "blue", size = 2) +
  geom_point(data = df %>% slice(1), color = "black", size = 3) +
  ggforce::geom_bezier(aes(group = i, color = i)) +
  geom_segment(
    data = segments, 
    aes(
      x = x_1, 
      xend = x_2, 
      y = y_1, 
      yend = y_2
    ), 
    linetype = "dotted", 
    color = "red"
  ) +
  coord_equal() +
  theme_minimal()
```

The black point represents the leaf base. This and the blue points denote the
start/end points of the bezier curves, and the red dots the positions of the
control points. The leaf is cut in two halves by the lines "4" and "4r" (which
are the same and represent the midvein of the leaf). The indices `i` which end on
"r" denote the upper half of the leaf. The exact dimensions of these coordinates
are generated by random numbers in certain ranges (see the definition of
`benjamini_leaf()`).


## Illustration of the randomness

In order to show the variations of the `benjamini_leaf()` (if parameters are not
explicitly specified), let's only pass the position of the leaf bases and let
the function randomly generate the rest of the shapes:

```{r plotlotsofbenjamini}
dfb <- expand_grid(
    x = seq(0, 200, 50),
    y = seq(25, 125, 25)
) %>%
  transpose() %>%
  map_dfr(~benjamini_leaf(gen_leaf_parameters(.x$x, .x$y)), .id = "leaf") %>%
  unite(i, i, leaf)

ggplot(dfb) +
  ggforce::geom_bezier(aes(x = x, y = y, group = i)) +
  # geom_point(data = l_points %>% bind_rows(), aes(x = x, y = y), color = "red") +
  coord_equal() +
  theme_minimal()
```


