---
title: "Create polygons from benjamini leaves"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Create polygons from benjamini leaves}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

In this vignette we'll have a look how the leaves represented by the bezier 
structures of `benjamini_leaf()` can be transformed to polygons.

Let's first load the necessary packages:


```{r setup, message=FALSE}
library(ggbenjamini)
library(dplyr)
library(purrr)
library(tidyr)
library(ggplot2)
library(stringr)

set.seed(123)
```

Now we'll create a data structure consisting of multiple bezier curves that we can use to grow branches after (DON'T TRY TO UNDERSTAND THIS CODE! I'M SURE YOU COULD DO THAT MUCH BETTER...):

```{r}
size <- 160
# df_branches <- tibble(
#   x = sample(1:size, 20, replace = TRUE), 
#   y = sample(1:size, 20, replace = TRUE), 
#   bezier_idx = rep(1:5, each = 4)
# )
xo = seq(-size/2, size/2, by = size/8) * 0.8
xm1 = xo * 0.75 - size/4
xm2 = xo * 0.75 + size/4
xu = xo * 0.5
y = rep(c(0.9, 0.5, 0.5, 0.1) * size, length(xo))
f <- function(xu, xm1, xm2, xo, y) {
  tibble(xu, xm1, xm2, xo) %>% 
    mutate(bezier_idx = row_number()) %>% 
    pivot_longer(-bezier_idx, values_to = "x") %>% 
    mutate(y = y) %>% 
    mutate()
}
df_branches <- f(xu, xm1, xm2, xo, y) %>% 
  mutate(x = x + size/2) %>% 
  mutate_at(
    c("x", "y"), 
    ~ .x + sample(
      (-size/20):(size/20), 
      length(xo), 
      replace = FALSE
    )
  )
df_branches
```

Now we can grow leaves on these branches:

```{r}
df_branches_and_leaves <- df_branches %>% 
  group_split(bezier_idx) %>% 
  map_dfr(
    ~benjamini_branch(df_branch = .x[c("x", "y")]),
    .id = "bezier_idx"
  )
```

When we plot these bezier curves with ggplot2, we can color the outlines of the
different elements:

```{r}
df_branches_and_leaves %>%
  unite(idx, bezier_idx, i_branch, i_part, element, remove = FALSE) %>% 
  ggplot(aes(x = x, y = y, group = idx, color = factor(bezier_idx))) + 
  ggforce::geom_bezier2(show.legend = FALSE) +
  scale_y_reverse() +
  theme_void()
```

If we want to fill these shapes with color we can first approximate the bezier curves with piecewise linear curves of length `n = 100` for each bezier. Furthermore, we'll add some simplex noise to make them look more interesting:
```{r}
df2 <- df_branches_and_leaves %>%
  unite(idx, bezier_idx, i_branch, element, remove = FALSE) %>%
  gen_leaf_bezier_coords(idx, bezier_idx, i_branch, element, i_part, n = 100) %>% 
  mutate(
    x2 = x + ambient::gen_simplex(x, y, frequency = 0.05, seed = 123),
    y2 = y + ambient::gen_simplex(x, y, frequency = 0.05, seed = 123)
  )
```

Now we can plot them with `ggplot2`s `geom_path()` for the branch and the leaf stalks and `geom_polygon()` for the 2 leaf halves.


```{r}
ggplot(
  data = df2 %>% 
    filter(str_detect(element, "^half [12]$")),
  aes(x = x2, y = y2, group = idx, fill = factor(idx))
) + 
  geom_path(
    data = df2 %>% 
      filter(!str_detect(element, "^half [12]$")), 
    aes(x = x2, y = y2, group = idx), 
    show.legend = FALSE, 
    color = "black"
  ) +
  geom_polygon(show.legend = FALSE, color = "black") +
  scale_y_reverse() +
  theme_void() 
```

If you look closely, you'll see that the leaves cover all leaf stalks and branches. This happens because in the ggplot, we first plot all pathes and then all polygons.
