---
title: "Import bezier pathes from svg files"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Import bezier pathes from svg files}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

*Hacky and a bit off-topic...*

This vignette shows how you can import bezier path data from an svg file and
then transform the format to the one needed by `ggforce::geom_bezier()`. Unless
you really want to import bezier pathes from your svg file s, it might not be of
huge interest. What's cool is that you can then draw pathes with svg software
such as inkscape.  The resulting dataframe `df_bezier_skeleton` of this vignette
is also included in the package. If you're not interested in importing shapes from
svg files you can just have a look how this data can be used in `vignette("create_benjamini_svg")` very result in
a data frame of the svg file

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(ggbenjamini)
library(dplyr)
library(purrr)
library(tidyr)
library(ggplot2)
library(ggforce)
library(minisvg)
```


## Load the skeleton from the svg file

There is an svg file included in the package that will serve as a skeleton of branches that we'll grow the leaves on (*This file was created with inkscape and then transformed with svgcairo to be in the needed format for the following code.*). Let's import it:


```{r}
svg_skeleton <- system.file("extdata", "branch_skeleton.svg", package = "ggbenjamini")
```


## svg beziers to dataframe 

Next we'll load the svg object and extract the bezier curves into a dataframe `df_svg_skeleton`:


```{r}
svg_doc <- parse_svg_doc(svg_skeleton)

# you can descend in the elements of the object and find the part you're
# interested in. For this file we can extract our bezier pathes with:
pathes <- svg_doc$child$g[[1]]$child$path

path_strings <- map_chr(pathes, ~.x$attribs$d)


df_raw <- tibble(s = path_strings) %>%
  mutate(row = row_number()) %>%
  # separate the 2 parts of each curve
  separate_rows(s, sep = "(?=[mMcC] )") %>%
  filter(s != "") %>%
  separate(s, c("svg_point_type", "coords"), sep = " ", extra = "merge") %>%
  separate_rows(coords, sep = " ") %>%
  filter(coords != "") %>%
  mutate(coords = as.numeric(coords)) %>%
  mutate(i = ifelse(row_number() %% 2 == 1, "x", "y")) %>%
  pivot_wider(values_from = coords, names_from = i) %>%
  unnest(x, y)

split_beziers <- function(df_bezier) {
  if (!nrow(df_bezier) != 4 | !(nrow(df_bezier) - 1)  %% 3 == 0) {
    stop("urgh")
  }
  if (nrow(df_bezier) > 4) {
    n_others <- (nrow(df_bezier) - 4) / 3
    other_rows <- map(1:(n_others+1), ~ 1:4 + (.x - 1) * 3) %>% unlist()
    res <- df_bezier[c(other_rows),] %>% mutate(i_curve = rep(1:(n_others+1), each = 4))
  }
  if (nrow(df_bezier) == 4) {
    res <- df_bezier
  }
  res
}

(df_svg_skeleton <- df_raw %>%
  group_by(row) %>% 
  summarise(split_beziers(cur_data()))
)
```

Looking at the `geom_bezier()` plot, 

```{r}
df_svg_skeleton %>%
  # arrange(-row_number()) %>%
  ggplot(aes(x, y, group = interaction(row, i_curve), color = factor(row))) +
  ggforce::geom_bezier(arrow = grid::arrow()) + scale_y_reverse()
```


it's as needed, but every second bezier is pointing in the wrong direction and the bezier group indices are not very important. Let's correct this:


## Cleaning up

```{r}
df_bezier_skeleton <- df_svg_skeleton %>%
  mutate(i = paste0(row, "_", i_curve)) %>% 
  group_by(row, i_curve) %>%
  # correct direction of beziers with index i_curve == 1:
  slice(ifelse(i_curve %% 2 == 1, 4:1, 1:4)) %>% 
  # get rid of the pairing indices of this svg file and replace with
  # i_branch for each branch (only for clarity):
  mutate(i_branch = cur_group_id()) %>%
  ungroup() %>%
  select(-row, -i_curve)

```

Now this looks better.

```{r}
df_bezier_skeleton %>%
  ggplot(aes(x, y, group = i_branch, color = factor(i_branch))) +
  ggforce::geom_bezier(arrow = grid::arrow()) + scale_y_reverse()

```

## `usethis::use_data()`

We'll store this dataframe in the package.

```{r}
usethis::use_data(df_bezier_skeleton, overwrite = TRUE)
```

